Worflow

### 2017-05-31 R/workflow.Rmd
add data

```{r examineMergeClusters, eval=FALSE}
#re-does merging simpling to make plot 
mergeClusters(ceObj, mergeMethod = "locfdr", plot="mergeMethod",cutoff = 0.01)
```

```{r heatmap,eval=FALSE}
plotHeatmap(ceObj, clusterSamplesData="dendrogramValue", breaks = .99)
```

>>>>

```{r examineMergeClusters, eval=FALSE}
#re-does merging simpling to make plot 
if(packageVersion("clusterExperiment")>='1.3.0.9001') mergeClusters(ceObj, mergeMethod = "locfdr", plotInfo="mergeMethod",cutoff = 0.01)
```

```{r heatmap,eval=FALSE}
if(packageVersion("clusterExperiment")>='1.3.0.9002') plotHeatmap(ceObj, clusterSamplesData="dendrogramValue", breaks = .99)
```
